Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Remove commented packages
Fix up introduction section

% alternative font if you prefer
%\usepackage{times}

% for alternative page numbering use the following package
% and see documentation for commands
%\usepackage{fancyheadings}

% other potentially useful packages
%\uspackage{amssymb,amsmath}
%\usepackage{url}
%\usepackage{fancyvrb}
%\usepackage[final]{pdfpages}

@@

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract - while 
performing maintenance on a car engine or on some electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is just characters in some file that gets compiled/interpreted to machine
code by other components which run on the operating system that, in turn,
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.

Having discussed about the high level of abstraction computers expose to 
their human operators, developing software that runs and performs as expected
in agreement with its requirements is not trivial. Thus, developers have
created software called \emph{issue tracking systems} that can manage
and track \emph{tickets}, which can take various forms, such as bug 
reports, feature requests etc. The aforementioned tickets can vary greatly
and issue tracking systems usually allow developers to include many 
types of information, such as:
  \begin{itemize}
    \item stack traces;
    \item steps to reproduce a bug;
    \item summary and description;
    \item story points (e.g. how many units of time does it take one
      developer to mark the ticket as resolved or completed).
  \end{itemize}
In order to create such tickets, the end users or the developers 
themselves notice certain flaws in the software or propose new features
to be implemented. Then, they head to the issue tracking system and 
create tickets where they provide information wrapped up in a ticket.
However, we are facing a main issue here, and that is what do developers 
on the project find most important when fixing a bug/implementing a 
new feature.

Therefore, a software engineering issue still not completely resolved
is how can one create valuable, high quality tickets?

@@

This research is trying to investigate what makes for a high quality 
ticket. More specifically, we are looking into the various components 
of a ticket (e.g. summary, description, comments) and their characteristics
in order to infer what combination of such components or what specific
attributes help developers close the ticket quicker (i.e. time between
ticket creation and when it is marked as CLOSED or RESOLVED).

We believe that this study is valuable to the software engineering 
community because solving the issue/ticket quality problem will help
reduce both cost and effort in companies worldwide. 
Having a clear understanding of what attributes make for 
a high quality ticket will lead the project maintainers to write  
specific guidelines in the ticket creation form (maybe even create an 
automated system) that will help reporters include the most
important details and structure them accordingly (e.g. for a specific
type of project it might be essential to include stack traces so that
developers can locate the bugs quicker), thus reducing the developers
and triagers' effort as well as reducing costs for the companies.

Furthermore, our study might also increase the likelihood of people
reporting bugs or asking for features more often. Not having specific 
guidelines or an automated system when creating a ticket many 
non-technical users might be put off and give up creating the report. 
However, if the company would put up a form where all the information
needed can be very easily inserted, users might be more inclined 
to report bugs and create feature requests, thus increasing the 
software's overall quality on the long term.

@@

However, as this is a broad research question, we have divided it into
two sub-research questions which, when combined, would yield the 
answer to our main research question:
  \begin{itemize}
    \item are there components which singularly affect the quality
      of a ticket (e.g. well written summary) or only combinations of them 
      (e.g. stack traces together with steps to reproduce)?
    \item how much do specific components or combinations of them 
      affect the quality of a ticket?
    \item can quality be inferred solely from the ticket or do we also
      need to consider the surrounding context (e.g. details related to
      the version control system)?
  \end{itemize}

@@

Moreover, another contribution that our study is trying to bring is that,
even though most studies so far have looked solely at ticket 
features/components, we want to inspect both tickets and other components
of the software project, such as version control system and how various
attributes affect the time-to-close for a particular ticket.

The third contribution that this research tries to achieve is to
propose a model for bug reports and/or feature requests. After collecting
data and finding which components together with their afferent attributes
make for a high quality ticket, we will propose a model for best practices
in terms of creating tickets.

>>>>

@@

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract - while 
performing maintenance on a car engine or on an electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is a multitude of layers on top of each other: it starts with a number of characters in some file;
then, that file gets compiled or interpreted to machine
code by other components which run on the operating system; then, these components
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and eventually perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.

As previously mentioned, there are many levels of abstraction that computers expose to 
their human operators, thus developing software that runs and performs as expected
in agreement with its requirements is not trivial. Therefore, developers have
created software called \emph{issue tracking systems} that can manage
and track \emph{tickets} of various forms such as bug 
reports, feature requests etc. The aforementioned tickets can vary greatly
and issue tracking systems usually allow developers to include many 
types of information, such as:
  \begin{itemize}
    \item stack traces;
    \item steps to reproduce a bug;
    \item summary and description;
    \item story points (e.g. how many units of time does it take one
      developer to mark the ticket as resolved or completed).
  \end{itemize}
In order to create such tickets, the end users or the developers 
themselves notice certain flaws in the software or propose new features
to be implemented. Then, they head to the issue tracking system and 
create tickets containing the necessary information.
However, we are facing a main issue here, and that is understanding the
key elements the developers look for when fixing a bug or implementing a 
new feature.

Therefore, a software engineering issue still not completely resolved
is how can one create valuable, high quality tickets.

@@

This research is investigating the features of a high quality ticket.
More specifically, it is looking into the various components 
of a ticket (e.g. summary, description, comments) and their characteristics
in order to infer what combination of such components or what specific
attributes help developers close the ticket quicker (i.e. time between
ticket creation and when it is marked as CLOSED or RESOLVED).

We believe that this study is valuable to the software engineering 
community because solving the issue/ticket quality problem will help
reduce both cost and effort in companies worldwide. 
Having a clear understanding of what attributes make for 
a high quality ticket will lead the project maintainers to write  
specific guidelines in the ticket creation form (maybe even create an 
automated system) that will help reporters include the most
important details and structure them accordingly (e.g. for a specific
type of project it might be essential to include stack traces so that
developers can locate the bugs quicker), which will in turn reduce
overall costs and developers/triagers' effort.

Furthermore, our study might also increase the likelihood of people
reporting bugs or asking for more specific features more often. Not having specific 
guidelines or an automated system when creating a ticket many 
non-technical users might be put off and give up creating the report. 
However, if the company would put up a form where all the information
needed can be very easily inserted, users might be more inclined 
to report bugs and create feature requests, thus increasing the 
software's overall quality on the long term.

@@

However, as this is a broad research question, we have divided it into
three sub-research questions which, when combined, would yield the 
answer to our main research question:
  \begin{itemize}
    \item are there components which singularly affect the quality
      of a ticket (e.g. well written summary) or only combinations of them 
      (e.g. stack traces together with steps to reproduce)?
    \item how much do specific components or combinations of them 
      affect the quality of a ticket?
    \item can quality be inferred solely from the ticket or do we also
      need to consider the surrounding context (e.g. details related to
      the version control system)?
  \end{itemize}

@@

Moreover, another contribution is that,
even though most studies so far have looked solely at ticket 
features/components, we want to inspect both tickets and other components
of the software project, such as version control system and how various
attributes affect the time-to-close for a particular ticket.

The third contribution is a proposed model for bug reports and/or feature requests.
After collecting data and finding which components together with their afferent attributes
make for a high quality ticket, we will propose a model for best practices
in terms of creating tickets.
